---
title: <br><br><center>BCN SAMPLE PROGRAMME<center>
author: "Your Company"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    thumbnails: false
    lightbox: true
    gallery: true
    css: form.css

---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r echo=FALSE, message=FALSE,warning=FALSE}
library(readxl)
library(dplyr)
library(knitr)
```

## Accommodation 🏨

### _**Main Hotel: Ohla Barcelona**_

**Ohla Barcelona** features rooms with contemporary decor and large windows. They all include a flat-screen TV, free WiFi and an iPod dock. The modern bathrooms come with bathrobes and slippers. Some rooms have views over the historic Gothic Quarter.
Romain Fornell is currently the head chef for all the culinary spaces at hotel Ohla Barcelona: Caelis restaurant, Vistro49, and La Plassohla. This last restaurant is specialised in catalan cuisine, offers tapas and small dishes. Guests can have a cocktail in the famous Ohla Boutique Bar.

The rooftop swimming pool offers fantastic city views with a chill out terrace. Other facilities at this hotel include a gym and a wellness area with a sauna.

The **Ohla Barcelona** is 300 m from Plaza Catalunya Square while Urquinaona Metro Station is only 200 m away. Passeig de Gracia Avenue and Gaudi's modernist buildings are 10 minutes' walk of the hotel. 

<img src = "https://r-fa.bstatic.com/images/hotel/max1024x768/148/148979532.jpg" width="365"> <img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/140/14017089.jpg" width="405" align="right"> 


<img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/141/14191840.jpg">

### **Alternative Hotels** {.tabset .tabset-fade .tabset-pills}

#### OD Barcelona

OD Barcelona features air-conditioned rooms with satellite flat-screen TV in the Eixample district of Barcelona. Boasting a 24-hour front desk, this hotel also provides guests with a seasonal outdoor pool. Guests can enjoy a selection of international cuisine in the in-house restaurant.

At the hotel, each room is fitted with a desk. Featuring a private bathroom, rooms at OD Barcelona also offer free WiFi. All guest rooms include a wardrobe.

Buffet and à la carte breakfast options are available every morning at the hotel.

Guests will have free access to Urquinaona Holmes Place Gym, 800 m from the hotel. 

<img src = "https://r-fa.bstatic.com/images/hotel/max1024x768/112/112393493.jpg" width="385"> <img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/112/112393525.jpg" width="385" align="right">

<img src = "https://r-fa.bstatic.com/images/hotel/max1024x768/112/112375607.jpg"> 



#### H10 Metropolitan

Featuring a rooftop terrace with a bar and chill-out pool, **H10 Metropolitan** is located in Barcelona, 90 m from Plaza Catalunya. It offers a tapas restaurant and free WiFi.

Each room has a flat-screen satellite TV, air conditioning, coffee machine and a minibar. The private bathroom comes with a hairdryer and bathrobes.

The **H10 Metropolitan** is located just 2 minutes' walk from Paseo de Gracia Avenue, with its boutique and designer fashion stores. The hotel is 700 m from Gaudi's La Pedrera, and you can walk to Las Ramblas in 3 minutes. 


<img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/161/161565881.jpg" width="367"> <img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/366/36604015.jpg" width="403" align="right">

<img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/366/36602949.jpg"> 

#### 1898 Hotel

Situated on Barcelona's famous La Rambla, this restored 19th-century building features a rooftop pool with a sun terrace. The elegant rooms include free Wi-Fi and a marble bathroom.
The colonial-style **Hotel 1898** has unique architectural and historical heritage which gives it the Speciality Monument status.

It features a stylish restaurant serving Mediterranean cuisine. It also offers a bar-restaurant with a terrace where guests can enjoy traditional tapas.
Plaza Catalunya is just 200 m from 1898 Hotel. Guests can also walk to the Gothic Quarter with its cathedral in 10 minutes. 


<img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/482/48273870.jpg" width="380"> <img src = "https://q-fa.bstatic.com/images/hotel/max1024x768/654/65423862.jpg" width="380" align="right">


<img src = "https://r-fa.bstatic.com/images/hotel/max1024x768/654/65408108.jpg"> 

## Map 🎯

<iframe src="https://www.google.com/maps/d/embed?mid=1aOlo3ab8vy_ufgAaIqFwU-O7NBsmc8vT&hl=es" width="800" height="550"></iframe>

## Programme 📆

### **Programme Overview and timeline**

```{r echo=FALSE, message=FALSE,warning=FALSE}
library(timevis)
library(dplyr)
library(readxl)

timeline <- read_excel("timeline.xlsx", sheet = "Sheet1", 
    col_types = c("date", 
        "text", "text", "numeric", "text", 
        "text"))

data <- data.frame( id = 1:length(timeline$start),
                    start = as.POSIXlt(timeline$start),
                    content = timeline$content,
                    group = timeline$group,
                    type = "box",
                    style = "background-color:#25a8f9;")

groups = data.frame(id = 1:4, content = c("Morning", "Lunch", "Afternoon", "Diner"))

tl <- timevis(data, groups, showZoom = TRUE, zoomFactor = 0.2, fit = TRUE, width = '100%', height = 400)

tl %>% setOptions(list(orientation = "top", align = "left"))

```



### **DAY 1** 

Cutting Edge Events staff will welcome the group at Barcelona airport and transfer the group to the chosen hotel. 

If it is possible we will do the check in or we left the luggage in hotel reception until check in time. Meanwhile, we will propose two activity options.

#### **Activity Options**{.tabset .tabset-fade .tabset-pills}

##### EBIKE BARCELONA 🚴

* **Duration:** 3 hours
* **Location:** Barcelona city centre
* **Minimum 10 pax - Máximum 100 pax**
* **Included:** 1 English speaking guide each 15-18 pax; helmet and Mineral water

The tour will start and finish next to Barcelona cathedral in Barcelona city center
The group will travel back in time to discover an unknown side of Barcelona through the eyes of Picasso, the most famous painter of the 20th century,
The city he fell in love with when he was just a teenager is still alive in his paintings and in its streets.
We will get on the eBikes and stroll around the alleys of the Gothic and Born quarters to follow his footsteps. Then, we will pass the exotic 19th-century Park de la Ciutadella from where we will bike straight to Barceloneta beach. On a bike lane beneath palm trees next to the beach, we will cross the Old Port back to the Old Town.

While riding through old backstreets and modern neighborhoods the grooup will get to know some of the most vivid contrasts that Barcelona has to offer. And by the end of the tour, they will have the impression to have experienced the changes Barcelona has gone through and have felt at the same time the exciting city Picasso used to know.

Possible route of the tour: 
<img src = "https://www.barcelonaebikes.com/wp-content/uploads/2016/03/pl%C3%A0nol-bohemian-eBike-low-1030x728.jpg" width="800">

<img src = "https://happytovisit.com/glib/3/barcelona-ebike-tour-4-7202.png" width="800">


##### BARCELONA FROM THE AIR 🚠

* **Duration:** 2,5H - 3 hours
* **Location:** Barcelona cable cars
* **Minimum 10 pax - Máximum 100 pax**
* **Included:** 1 English speaking guide, a 30 seater coach at disposal for the activity, tickets for the 2 cable cars.  

The bus will go trough the port area to **Montjuic** and the Olympic area seeing Palau Sant Jordi and the stadium, then they will stop at the Grey Cable car station. This **Cable car** will transfer guests to the Castle. Our guide will explain guests the history of all the area and the castle. From there they will walk to Miramar where they will find the Red Cable Car. This is the oldest cable car of the city and it offers a great panoramic view of the city - a unique experience -
Each cable car is up to 18 pax - this cable car can’t be booked in advance or privatized. The **Red Cable Car** ends at the Old Port (is the same tower as the restaurant Torre de Alta Mar). Once everyone will be at Port Station they will be picked up by the bus that will transfer them to the hotel.

<img src = "https://www.webarcelona.net/sites/default/files/teleferico-montjuic_0.jpg" width="428"> <img src = "https://www.lavanguardia.com/r/GODO/LV/p3/WebSite/2016/09/09/Recortada/LAVANGUARDIA_G_3640423-162-kxzD-U41198934917QR-992x558@LaVanguardia-Web.jpg" width="341" align="right">

<img src = "https://media-edg.barcelona.cat/wp-content/uploads/2015/05/1-2-3-2-10-DISE-Vista-panor%C3%A0mica-de-Barcelona-10-3-14-HEMAV-12.jpg" width="800">



#### **Lunch Restaurant Options**  🍽  {.tabset .tabset-fade .tabset-pills}

After the activity guests will have some time for lunch, We offer 2 restaurant options located in the city centre to offer guests the opportunity to spend some free time for shopping after lunch. 

##### CASA CARMEN

* **Location:** Barcelona city centre
* **Cuisine** Mediterranean, Small plates and half portions, Fusion cooking

Casa Carmen arrives at Barcelona's city center in 2017 with a very attractive proposal: a Mediterranean menu with both traditional and innovative dishes at affordable prices. In addition, it also has an interesting selection of tapas and dishes perfect to share. The restaurant, very cozy, is divided into two floors and has different spaces ideal for all kinds of celebrations and group events.

<img src = "http://2012.coop/wp-content/uploads/2017/08/restaurante-casa-carmen.jpg" width="800">


##### RACO DE NURIA

* **Location:** Barcelona city centre
* **Cuisine** Tapas, Mediterranean Flavour
* **Capacity** First floor 70 pax


In classical mythology, Bacchus was the god of wine, ritual madness and religious ecstasy. That's why at this restaurant, will raise you up a few metres above street level. To be precise, the first floor above La Rambla where it merges with Plaça Catalunya.

Down below... the world, the lights, the hustle-and-bustle and the everyday comings and goings of Barcelona. Up above... the pleasure of flavours, smells, colours, ingredients and serenity.

A simply divine location, menu and space.

<img src = "https://media-cdn.tripadvisor.com/media/photo-s/12/4e/60/ef/raco-del-nuria.jpg" width="800">


#### **Dinner Restaurant Options** 🍽 {.tabset .tabset-fade .tabset-pills}

After some free time to refresh, guests will enjoy their first evening in the city.

##### Windsor

* **Location:** Eixample Esquerre.
* **Cuisine** Season cuisine, Catalan


Located in a beautiful Catalan Modernist building for two decades, Windsor provides the most special setting to enjoy the updated Catalan haute cuisine by young chef Carlos Alconchel, who works with selected seasonal products of proximity. The space -elegant, contemporary and flooded with natural light- has a great terrace and different private dining rooms.

You can see it as if you were there with this virtual tour:

<iframe src="https://www.google.com/maps/embed?pb=!4v1559131575239!6m8!1m7!1sA1d4k9whYbQAAAQfCSqdJw!2m2!1d41.3946548524256!2d2.157238657469634!3f63.231585570879126!4f-9.87162869673216!5f0.8160813932612223" width="800" height="500" frameborder="1" style="border:1" allowfullscreen></iframe>

##### Barceloneta

* **Location:** Old Harbour
* **Cuisine** Fish and rice dishes, Catalan Cuisine

Located just next to the yatch marina, this is a beautifull restaurant specialized in fish and rice dishes. Their food is elaborated with fresh, high quality ingredients.
It has a big terrace and different dining rooms.

You can see it as if you were there with this virtual tour:

<iframe width="100%" height="480px" src="https://poly.google.com/view/1c2KgAOLnNY/embed?chrome=min" frameborder="0" style="border:none;" allowvr="yes" allow="vr; xr; accelerometer; magnetometer; gyroscope; autoplay;" allowfullscreen mozallowfullscreen="true" webkitallowfullscreen="true" onmousewheel="" ></iframe>


### **DAY 2** 

After breakfast, we will do check out and our bus will be waiting for us next to the hotel door. We will depart, luggage included to the Penedes region, famose for the best Cavas and most of the best wines of the country. We will do our activities in a very special winery **Jean Leon**, which belongs to Torres group, consider the second  World’s Most Admired Wine Brand 2019 by the English publication: Drinks International. 

#### **JEAN LEON** 🍷

* **Location** Jean Leon Winery - Penedes region
* **Duration** 3 hours plus meal  
* **Capacity** Minimum 10pax - maximum 150pax 
* **Included** Bus, activity according client wishes, meal and wine tasting

**Jean Leon** invites the visitors to discover the story of an extraordinary man who was ahead of his time. Thanks to his unique vision, he triumphed in Hollywood and achieved his dream of creating a signature wine 

<iframe width="800" height="500" src="https://www.youtube.com/embed/OyDeLQsdS94" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>


Once we arrive we will do a **Scooter bike ride**  to Discover Jean Leon wine estate in a fun, easy and sustainable way"
Explore Jean Leon vineyards and enhoy the beautiful landscape in the most comfortable, envirnmentally friendly and fun way possible: on an electric bicycle! 

Once the group will finish, we will our **paella cooking class** "al fresco" in winery gardens,  if the weather is nice or indoor in the glass room overlooking Penedes valley, followed  by the wine tasting (3 wines)

<img src = "https://bussatravel.com/uploads/images/tour/c368f7c41dd8.jpg" width="410">
<img src = "https://www.jeanleon.com/wp-content/uploads/2018/02/patinete-2.jpg" width="380" align="right">

<img src = "https://cdn1.es.yumping.info/emp/fotos/4/5/6/5/tb_e-19634565-22792292-2010412009245699-4616590512794143747-o15399393978817.jpg">

After the wine tasting, we will take our bus, which transfer the group to Barcelona airport for departures

END OF THE PROGRAMME

*****

## Terms & Conditions ☑

  * Your terms
  
*****





